---
title: "p8105_hw5"
author: "Tom Carpino, tc2899"
date: "November 8, 2018"
output: html_document
---

This homework flexes our skills on iteration and graphing. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

### Problem 1: Case Control Study 

* The format of this problem involves the following: 
    + Importing the dataset
    + Tidying the dataset and creating a usable dataframe 
    + Creating a spaghetti plot 

* I loaded the following packages, using the suppressMessages function: 
    + tidyverse
    + plotly
    + rvest
    + magrittr

```{r echo = FALSE}
suppressMessages(library(tidyverse))
suppressMessages(library(plotly))
suppressMessages(library(rvest))
suppressMessages(library(magrittr))
```

Listing Files 
```{r}
listed_files = tibble(filepath = list.files("./data/", pattern = "*.csv", full.names = TRUE),
                         filename = basename(filepath))
```

Writing a function to read the data: 

```{r}
read_fx = function(data){
  read_csv(file = data)
}
```

Creating the dataframe using a `map` function: 

```{r, message = FALSE}
df_patient = 
  listed_files %>% 
  mutate(data =  purrr::map(listed_files$filepath, read_fx)) %>% 
  unnest() %>% 
  select(-filepath) %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  mutate(
    id = str_replace(filename, ".csv",""), 
    week = as.numeric(str_replace(week, "week_", ""))) %>% 
  separate(id, into = c("group", "id"), sep = "_") %>% 
  mutate(id = as.factor(id))

df_patient
```

Creating the Spaghetti Plot: 
```{r spaghetti}
ggplot(
  df_patient, 
  aes(x = week, y = value, color = id, group = id)) + 
  geom_line() +
  facet_grid(~group) +
  labs(
    title = "Observations Over 8 Weeks", 
    x = "Week", 
    y = "Observation", 
    color = "Participant") + 
    viridis::scale_color_viridis(discrete = TRUE)
```

Here one can observe a stark difference in outcomes between the control group, con, and the experimental group, exp. It is clear that the values for the control group remain relatively constant between -1.25 and 3.75 over the course of the 8 weeks, whereas the observation values steadily increase over time from weeks 0 to 8 in the experimental group.  

### Problem 2: Homicide in Large Cities 

* The format of this problem involves the following: 
    + Using the existing repo
    + Describing data 
    + Using functions to estimate crime rates
    + Creating plots with CIs

```{r homicide_data}
homicide = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>% 
  mutate(city_state = str_c(city, ",", " ", state))
```

#### Description 
The dataset pulled from the _Washington Post_ has **`r nrow(homicide)`** observations across **`r ncol(homicide)`** variables that include information about the location (latitude and longitude) of the homicide and the victim (first and last name, age, sex, race).  

#### Estimating Homicide Rates in Baltimore

Here I am summarizing within the cities the disposition variable (closed or open cases with no arrests): 
```{r}
sum_cities = homicide %>% 
  mutate(disposition = fct_collapse(homicide$disposition, "No arrest" = c("Closed without arrest","Open/No arrest"))) %>% group_by(city_state) %>% 
  count(disposition) %>% 
  spread(key = disposition, value = n) %>% 
  janitor::clean_names() %>% 
  mutate(total = closed_by_arrest + no_arrest)
```

Here I am using the prop.test function to estimate the propportion of homicides that are unsolved in Baltimore using the *sum_cities* dataframe I just created. 

```{r}
bmore = sum_cities %>% filter(city_state == "Baltimore, MD")
bmore_disp = prop.test(bmore$no_arrest, bmore$total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  janitor::clean_names() %>% 
  knitr::kable()
bmore_disp
```

This finds that approximately 64.55% of all of the cases of homicides in Baltimore do not have any arrests, with the lower estimate being 62.75% and the upper estimate being 66.31%. This is scary. 

```{r all_cities}

prop_test = function(unsolved, sum_cities) {
  prop.test(unsolved, sum_cities) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
}

all_cities_unnested = sum_cities %>% group_by(city_state) %>% nest() %>% 
  mutate(estimate_ci = map(data, prop_test)) %>% unnest() %>% 
  mutate(city_state = reorder(city_state, estimate)) %>% janitor::clean_names()

```


```


